Supplementary Information

### 2021-08-27 doc/manuscript/ForestGEO_treerings_SI.Rmd
knit names with authorities into Table S2
.... still needs some formatting

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S2 <- read.csv("tables_figures/species.csv", col.names = c("species code", "family","latin name", "sites sampled", "leaf type", "leaf phenology", "light requirements*", "bark allometry**"), stringsAsFactors = FALSE, check.names = FALSE)
kable(S2, format = "latex", booktabs = TRUE,  escape = F, linesep = c('\\addlinespace'))%>%
  row_spec(0, italic = F, bold = T) %>%
  column_spec(3, italic = T) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) 
```
*For extratropical species, light requirements are classified based on the database of @niinemets_tolerance_2006. For tropical species, categorization is based on @alfaro-sanchez_growth_2017 for BCNM and @vlam_temperature_2014 for HKK.

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S2 <- read.csv("tables_figures/species.csv",  
               col.names = c("species code", "family", "x", "latin name", "sites sampled", "leaf type", "leaf phenology", "light requirements*", "bark allometry**"),
               stringsAsFactors = FALSE, check.names = FALSE)
S2 <- subset(S2, select = -c(x)) 
kable(S2, format = "latex", booktabs = TRUE,  escape = F, linesep = c('\\addlinespace'))%>%
  row_spec(0, italic = F, bold = T) %>%
  column_spec(3, italic = T) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) 
```
*For extratropical species, light requirements are classified based on the database of @niinemets_tolerance_2006. For tropical species, categorization is based on @alfaro-sanchez_growth_2017 for BCNM and @vlam_temperature_2014 for HKK.
